---
title: "grading"
format: html
---

```{r}
#| echo: false
#| output: false

library(tidyverse)
library(lubridate)
library(stevemisc)
library(kableExtra)

```


```{r}
#| echo: false
#| output: true
#| warning: false

# Ref: http://svmiller.com/blog/2020/08/a-ggplot-calendar-for-your-semester/

quarter_dates <- c(ymd(20251206),
  seq(ymd(20250918), ymd(20251205), by=1)
)
class_wdays <- c("Mon", "Tue", "Wed", "Thu")

not_here_dates <- c(
  ymd("20251111"),
  seq(ymd(20251124), ymd(20251128), by=1)
)

exam_dates <- c(ymd(20251016), ymd(20251206))

project_dates <- ymd(20251113)

finals_week <- seq(ymd(20251208), ymd(20251212), by = 1)

# Create a data frame of dates, assign to Cal
Cal <- tibble(date = seq(ymd(20250901), ymd(20251231), by=1))  |>
  mutate(mon = lubridate::month(date, label = T, abbr = F),
         wkdy = weekdays(date, abbreviate = T),
         wkdy = fct_relevel(wkdy, "Sun", "Mon", "Tue", "Wed", "Thu", "Fri", "Sat"),
         quarter = date %in% quarter_dates, 
         project = date %in% project_dates,
         exam = date %in% exam_dates,
         not_here = date %in% not_here_dates, # Academic Holidays at Cal Poly
         exam_wk = date %in% finals_week,
         day = lubridate::mday(date), 
         week = wom(date)
         ) |>
  mutate(category = case_when(
    project ~ "Project Due",
    exam ~ "Exam (In-Class)",
    not_here ~ "Cal Poly Holiday",
    quarter & wkdy %in% class_wdays & !not_here & !exam_wk | date == "2023-03-18" ~ "Class Day",
    TRUE ~ "NA")
  )

class_cal <- Cal |> 
  ggplot(aes(wkdy, week)) +
  theme_bw() +
  theme(aspect.ratio = 0.5, 
        panel.grid.major.x = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank(),
        axis.title.y = element_blank(), 
        axis.title.x = element_blank(),
        axis.ticks.y = element_blank(), 
        axis.text.y = element_blank()) +
  geom_tile(alpha= 1, aes(fill=category), color="black", linewidth=.45) +
  facet_wrap(~mon, scales = "free", ncol=2) +
  geom_text(aes(label = day, color = quarter & (!not_here))) +
  scale_y_reverse(breaks=NULL) +
  scale_color_manual(values = c("FALSE" = "#E4E3D3", "TRUE" = "black"), guide = "none") + 
  scale_fill_manual(values=c("Class Day" = "#154734", 
                             "Exam (In-Class)" = "#D0DF00",
                             "Project Due" = "#FF6A39",
                             "Cal Poly Holiday" = "#BD8B13",
                             "NA" = "white"),
                    breaks=c("Class Day", "Cal Poly Holiday", "Exam (In-Class)", "Project Due"))
class_cal
```


### Grading

<div class="custom-table">
  <style>
    .custom-table table {
      width: 100%;
      border-collapse: collapse;
      margin: 20px auto; /* Center the table */
    }

    .custom-table th, .custom-table td {
      border: 1px solid #dddddd;
      text-align: justify;
      padding: 12px;
    }

    .custom-table tr:nth-child(1) {
      background-color: #ffffff;
    }

    .custom-table tr:nth-child(2) {
      background-color: #e1bee7; /* Light shade for 10% */
    }

    .custom-table tr:nth-child(3) {
      background-color: #ce93d8; /* Medium shade for 15% */
    }

    .custom-table tr:nth-child(4) {
      background-color: #ce93d8; /* Medium shade for 15% */
    }

    .custom-table tr:nth-child(5) {
      background-color: #ce93d8; /* Medium shade for 15% */
    }

    .custom-table tr:nth-child(6) {
      background-color: #ce93d8; /* Medium shade for 15% */
    }

    .custom-table tr:nth-child(7) {
      background-color: #ab47bc; /* Darkest shade for 30% */
    }

    .custom-table tr:nth-child(8) {
      background-color: #9c27b0; /* Total row */
      color: #ffffff;
    }
  </style>

  <table>
    <tr>
      <th>Assessment</th>
      <th>Percentage</th>
    </tr>
    <tr>
      <td>Weekly Assignments (Individual, Take Home)</td>
      <td>10%</td>
    </tr>
    <tr>
      <td>Midterm 1 (Individual, In-class)</td>
      <td>15%</td>
    </tr>
    <tr>
      <td>Project Presentation (Group, Take Home)</td>
      <td>15%</td>
    </tr>
    <tr>
      <td>Lab Assignments (Group)</td>
      <td>15%</td>
    </tr>
    <tr>
      <td>Investigation Assignments (Group)</td>
      <td>15%</td>
    </tr>
    <tr>
      <td>Final Exam</td>
      <td>30%</td>
    </tr>
    <tr>
      <td>Total</td>
      <td>100%</td>
    </tr>
  </table>
</div>

### Letter Grades

Your final grades will be determined based on the total points earned. It's essential to review the letter grades outlined below for a clear understanding of the grading criteria. __Please be aware that I will not "round up" grades at the end of the quarter.__


<html lang="en">
<head>
  <meta charset="UTF-8">
  <meta name="viewport" content="width=device-width, initial-scale=1.0">
  <style>
    .no-color-table table {
      width: 100%;
      border-collapse: collapse;
      margin: 20px auto; /* Center the table */
    }
    .no-color-table th, .no-color-table td {
      border: 1px solid #dddddd;
      text-align: left;
      padding: 8px;
      background-color: transparent; /* Set background color to transparent */
    }
  </style>
</head>
<body>

<table class="no-color-table">
  <tr>
    <th>Letter Grade</th>
    <th>Points</th>
  </tr>
  <tr>
    <td>$A$</td>
    <td>$93 \le x$</td>
  </tr>
  <tr>
    <td>$A^-$</td>
    <td>$90 \le x < 93$</td>
  </tr>
  <tr>
    <td>$B^+$</td>
    <td>$87 \le x < 90$</td>
  </tr>
  <tr>
    <td>$B$</td>
    <td>$83 \le x < 87$</td>
  </tr>
  <tr>
    <td>$B^-$</td>
    <td>$80 \le x < 83$</td>
  </tr>
  <tr>
    <td>$C^+$</td>
    <td>$77 \le x < 80$</td>
  </tr>
  <tr>
    <td>$C$</td>
    <td>$73 \le x < 77$</td>
  </tr>
  <tr>
    <td>$C^-$</td>
    <td>$70 \le x < 73$</td>
  </tr>
  <tr>
    <td>$D^+$</td>
    <td>$67 \le x < 70$</td>
  </tr>
  <tr>
    <td>$D$</td>
    <td>$63 \le x < 67$</td>
  </tr>
  <tr>
    <td>$D^-$</td>
    <td>$60 \le x < 63$</td>
  </tr>
  <tr>
    <td>$F$</td>
    <td>$x < 60$</td>
  </tr>
</table>

</body>
</html>

