---
title: "STAT 218 Lab Assignment 4"
subtitle: "Week 6 Lecture 4 Lab 4"
author: 
  - "Team Member 1: NAME HERE"
  - "Team Member 2: NAME HERE"
  - "Team Member 3: NAME HERE"
date: today
date-format: "MMMM D[<sup style='font-size:65%;'>th</sup>], YYYY"
format: pdf
execute:
  echo: true
---

## Lab Assignment 4

In this assignment, we will work with an external data set. Make sure download the dataset (Example 8.3.4.csv) from Canvas as well.


Let's use `library` function and load the data sets that we will use today.

```{r}
#| output: false
library(tidyverse)
stream <- read_csv("stream.csv")
```


# Paired Samples _t_ test

__Example of a Case:__ Pollutants in a stream may accumulate or attenuate as water flows down the stream. In a study to monitor the accumulation and attenuation of fecal contamination in a stream running through cattle rangeland, monthly water specimens were collected at two locations along the stream over a period of 21 months.

The data set `stream` the total coliform count (MPN/100ml) for a water specimen.

__Question 1. What is the research question of this study?__


Type your answer here.


__Question 2. What type of variables do we have in this data set? Quantitative or categorical?__


_sample:_

_date:_

_upstream:_

_downstream:_

_difference:_


__Question 3. Please list the assumptions required for this test and check the assumption of normality for this study. Interpret the assumptions overall.__


_Random Sampling:_ Explain here.

_Independence of Observation:_ Explain here.

_Normal Distribution:_ Explain here.


- _This output is from a calculation of Shapiro-Wilk test. We generally use Shapiro-Wilk test for relatively smaller sample size because visuals can be misleading in smaller sample sizes. Please interpret Shapiro-Wilk $p$-value._


	Shapiro-Wilk normality test

data:  stream$Difference
W = 0.9641, p-value = 0.6022



Type your answer here.


__Directions of Question 4: Perform a paired sample $t$-test to assess whether the mean total coliform count is consistent across the two locations.__



__Question 4.1 Write out the null & the alternative hypotheses within the context of this study:__

Type your answer here.



__Question 4.2. Compute test statistic by running the code chuck below and explain what you see in the output.__

```{r}
t.test(stream$upstream, stream$downstream, paired = TRUE)
```


Type your answer here.


__Question 4.3: Run the code chuck below again and explain what you see in the output.__

```{r}

t.test(stream$difference, mu = 0)

```

Type your answer here.


__Question 4.4. Compare and contrast how the codes in Question 4.2 and Question 4.3 work. Comment on the p-value, test statistic, and confidence interval. If they produce the same results, explain what the two codes did differently.__


Type your answer here.


__Question 4.5. Draw conclusion and write a conclusion statement.__


Type your answer here. Comment on p-vale and confidence interval.








