---
title: "Ch. 6 & Ch. 7: Applications of $t$-tests"
subtitle: "STAT 218 - Week 6, Lecture 4 Lab 4"
format: 
  revealjs:
      theme: simple
      slide-number: true
      chalkboard: true
---


# What Have We Learned So Far?

## 
### A Snapshot
::: {style="font-size: 28px"}
- **Descriptive Statistics** describes and summarizes data.
  - Includes understanding 
    - distribution shape (skewed, normal, etc.), 
    - central tendency (mean, median, mode), and 
    - spread (variance, standard deviation, range).

- **Inferential Statistics** makes predictions and draws conclusions about populations based on sample data.
  - We saw different types of t-tests:
    - __One sample t-test:__ compares a sample mean to a known or hypothesized population mean.
    - __Independent samples t-test:__ compares means of two independent groups.

:::

##
### Estimation and Hypothesis Testing 
::: {style="font-size: 28px"}

We learned that we can estimate the unknown parameters in two ways:

- __Point estimation:__ A single value calculated from the sample (e.g., $\bar{y}$)

- __Confidence Intervals:__ A range of values within which the parameter is expected to fall, with a certain degree of confidence.(e.g., 95% CI, 90% CI)

We also learned that we can use hypothesis testing to test for a specific value(s) of the parameter.

- e.g., $H_0: \mu = 76$ cm & $H_A: \mu \neq 76$ cm (Two-tailed test)
- $H_0: \mu_1 - \mu_2 = 0$ cm  $H_A: \mu_1 > \mu_2$ (One-tailed test)
:::

# Hypothesis Testing Steps

## 
#### Introduction 

:::{.callout-important}

We can summarize hypothesis testing in five steps:

1. Construct the Hypotheses of $H_0$ and $H_A$
2. __Check the validity conditions/assumptions__ (We will see this today)
3. Compute test statistic and find the _p_-value (Interpreting R Output)
4. Draw conclusion.

:::

## 
### Assumptions - Validity Conditions
::: {style="font-size: 28px"}

- It is always important to check first whether the conditions are reasonable in a given case.
- Here is the list of conditions that we should be aware of for $t$-tests.

__1) Random Sampling:__ the data can be regarded as coming from independently chosen random sample(s),

__2) Independence of Observations:__ the observations should be independent, and

__3) Normal Distribution:__ Many of the methods depend on the data being from a population that has a normal distribution.

  - __REMEMBER!__ If sample size is large, then condition (3) is less important (Central Limit Theorem).

:::

## 
### Normality Assumption - I
::: {style="font-size: 28px"}

- If the only source of information is the data at hand, then normality can be roughly checked.  

  - Unfortunately, for a small or moderate sample size, this check is fairly rudimentary.
  - If the sample is large, then the visual plots (histogram and normal quantile plot) give us good information about the population shape; 
    - However, if $n$ is large, the requirement of normality is less important anyway due to the Central Limit Theorem.
- In any case, a rudimentary check is better than none, and every data analysis should begin with inspection of a graph of the data, with special attention to any observations that lie very far from the center of the distribution.

:::

## Normality Assumption - II

::: {style="font-size: 28px"}

We check assumptions/validity conditions before conducting any statistical analysis. To check normality assumption, we need to first check sample size.

- $1^{st}$ option - small samples: Check the $p$-value of Shapiro Wilk test. It is best used with a sample size less than 50 (Shapiro & Wilk 1965; Uttley,2019). 

- $2^{nd}$ option - large samples: Check the visual plots (e.g., histogram, normal quantile plot) if your sample size is more than 50.

Today we will have large samples so we will learn Shapiro-Wilk next week.

:::

# One Sample $t$-test


## 
### To-do List Before Start
::: {style="font-size: 26px"}

- Download the worksheet and from Canvas (Lab Assignment 4).  
- Save them to your STAT 218 folder.   
- Assign your roles.
  
_Project Manager:_

  - Follow the slides and give directions to the coder and note taker.
  - Facilitate communication within the group and with the instructor.

_Note Taker:_

  - Take notes on key findings, insights, and interpretations derived from the data and analyses.

_Coder:_

  - Lead the coding efforts, writing and managing the R scripts.
  - Ensure code quality, functionality, and documentation standards are met.

:::

## Introduction
::: {style="font-size: 28px"}

- In one sample $t$ tests, data collected from one sample and compares the mean score with a __test value__.
  - Test value can be   
  (1) reported previously in the literature; or   
  (2) found by calculating __level of chance__.

:::

## Introduction - II

- To begin with, we need `infer` package to conduct _t_ tests. 
- Let's run the code chunk in our lab assignment file and load `infer` package by using `install.packages()` function.


```{r}
#| eval: false
#| echo: true
#| output: false
install.packages("infer")
```


## Introduction - III


After loading that package, let's run `library` functions and load the data sets that we will use today.

```{r}
#| output: false
#| echo: true
library(tidyverse)
library(infer)
library(palmerpenguins)
data("penguins") 
```



## 

__Example of a Case:__ 

Imagine that you are a biologist studying penguins, particularly their bill lengths. You hypothesize that the average bill length of penguins is 40 mm and you collect a random sample of 344 penguins, measure and record their bill length in mm.

Perform a __one sample $t$-test__ to investigate whether the bill length of the penguins differs from the test value of 40 mm. 


##
### Instructions

Open the assignment file and answer the following questions.

<br>

__Question 1. What is the research question of this study?__

Type your answer in the assignment file.

<br>

__Question 2. What type of variable is used in this study?__

Type your answer in the assignment file.


## 
#### Question 3. Checking the Normality Assumption

<br>

- Check your sample size first! 
  - $n$ > 50, so we can check visual plots.
- _Direction:_ Please create a histogram to check the normality.



## Question 3. Quantile Plot


```{r}
#| echo: true
#| output: true
ggplot(data = na.omit(penguins),
       aes(sample = bill_length_mm)) +
  geom_qq()
```



## 
### Question 4. Interpreting the Output


```{r}
#| echo: true
#| output: true
t_test(penguins, response = bill_length_mm, mu = 40)
```

::: {style="font-size: 28px"}

__Conclusion:__ _Type your hypothesis testing conclusion to your assignment file!_

__Confidence Interval:__ _Type your confidence interval statement to your assignment file!_

:::

# Independent Samples $t$-test

## 
__Example of a Case:__ 

Now, you're curious about the difference in the body mass of penguins based on their sex. You hypothesize that body mass varies between different sexes. To test your hypothesis, you collect a random sample of 344 penguins, measure their body mass, and record their sex.

Perform an __independent samples $t$-test__ to investigate whether the body mass of penguins differs between different sexes.

##
### Instructions

Continue with the assignment file and answer the following questions.

__Question 1. What is the research question of this study?__

Type your answer in the assignment file.

__Question 2. What type of variable is used in this study?__

Type your answer in the assignment file.

## 
#### Question 3. Checking the Normality Assumption

- Check your sample size first! 
  - $n$ > 50, so we can check visual plots.
  

## 
### Question 3. Quantile Plots

```{r}
#| echo: true
#| output: true
ggplot(data = na.omit(penguins),
       aes(sample = body_mass_g)) +
  geom_qq() +
  facet_wrap(~sex)
```

## 
### Question 4. Interpreting the Output


```{r}
#| echo: true
#| output: true
t_test(x = penguins, 
       formula = body_mass_g ~ sex, 
       order = c("male", "female"),
       alternative = "two-sided",
       conf_level = 0.90)
```

::: {style="font-size: 28px"}

__Conclusion:__ _Type your hypothesis testing conclusion to your assignment file!_

__Confidence Interval:__ _Type your confidence interval statement to your assignment file!_

:::
