---
title: "STAT 218 Lab Assignment 4"
subtitle: "Week 6 Lecture 4 Lab 4"
author: 
  - "Team Member 1: NAME HERE"
  - "Team Member 2: NAME HERE"
  - "Team Member 3: NAME HERE"
date: today
date-format: "MMMM D[<sup style='font-size:65%;'>th</sup>], YYYY"
format: pdf
execute:
  echo: true
---

## Lab Assignment 4

Please run the code chunk below to download the necessary package you need.


```{r}
#| include: false
install.packages("infer" , repos = "http://cran.us.r-project.org")
```


Remember, we need to use library functions to be able to tell R which package we want to use right now. Please run the code chunk below too.

```{r}
#| output: false
library(infer)
library(tidyverse)
library(palmerpenguins)
data("penguins") 
```

__NOTE:__ Please ignore `penguins_raw` data for this class and USE `penguins` for this assignment.



# One Sample _t_ test

In this case, we will use `penguins` data set.
  
__Example of a Case:__ Imagine that you are a biologist studying penguins, particularly their bill lengths. You hypothesize that the average bill length of penguins is 40 mm and you collect a random sample of 344 penguins, measure and record their bill length in mm.



__Question 1. What is the research question of this study?__


Type your answer here.


__Question 2. What type of variable do we have in this study?__


Type your answer here.


__Question 3. Check the lecture slides and please list the assumptions required for this test and check the assumption of normality for this study. Interpret the assumptions overall.__


_Random Sampling:_ Explain here.


_Independence of Observation:_ Explain here.


_Normal Distribution:_ Explain here.



```{r}
# Type your codes here to check normality by using histogram. Find ggplot codes from our previous data viz lab slides for creating a HISTOGRAM.
```

Interpret your histogram here.



- _This code is for normal quantile plot._

```{r}
ggplot(data = na.omit(penguins),
       aes(sample = bill_length_mm)) +
  geom_qq()
```



Interpret the assumptions overall and type your reasoning.


__Directions for Question 4: Conduct a one sample $t$-test to investigate whether the bill length of the penguins differs from the test value of 40 mm. Answer the questions given below.__


__Question 4.1 Write out the null & the alternative hypotheses within the context of this study:__


Type your answer here.




__Question 4.2. Compute test statistic by running the code chuck below and explain what you see in the output.__

```{r}
t_test(penguins, response = bill_length_mm, mu = 40)

```

Type your answer here.


__Question 4.3. Draw conclusion and write a conclusion statement.Include p-value and confidence interval.__


Type your answer here.



# Independent Samples _t_ test

In this case, we will use again `penguins` data set.
  
__Example of a Case:__ Now, you're curious about the difference in the body mass of penguins based on their sex. You hypothesize that body mass varies between different sexes. To test your hypothesis, you collect a random sample of 344 penguins, measure their body mass, and record their sex.


__Question 1. What is the research question of this study?__


Type your answer here.


__Question 2. What type of variables do we have in this study?__


Type your answer here.


__Question 3. Again check the lecture slides and please list the assumptions required for this test and check the assumption of normality for this study. Interpret the assumptions overall.__

_Random Sampling:_ Explain here.

_Independence of Observation:_ Explain here.

_Normal Distribution:_ Explain here.


```{r}
# Type your codes here to check normality by using histogram. You can add facet_wrap(~sex) to see two histograms
```


- _This code is for normal quantile plot for both sexes._

```{r}
ggplot(data = na.omit(penguins),
       aes(sample = body_mass_g)) +
  geom_qq() +
  facet_wrap(~sex)

```



Interpret the assumptions and type your reasoning.




__Directions for Question 4: Conduct an independent samples $t$-test to investigate whether the body mass of penguins differs between different sexes.__


__Question 4.1 Write out the null & the alternative hypotheses within the context of this study:__

Type your answer here.



__Question 4.2. Compute test statistic by running the code chuck below and explain what you see in the output.__

```{r}
t_test(x = penguins, 
       formula = body_mass_g ~ sex, 
       order = c("male", "female"),
       alternative = "two-sided",
       conf_level = 0.90)
```



Type your answer here.


__Question 4.3. Explain what each function/argument does in this question.__

`t_test`: Type your answer here.

`formula`:Type your answer here.

`order`: Type your answer here.

`alternative`: Type your answer here.

`conf.level`: Type your answer here.


__Question 4.4. Draw conclusion and write a conclusion statement. Include p-value and confidence interval interpretations.__


Type your answer here.


