---
title: "One Way ANOVA - Lab 5 Assignment"
subtitle: "Week 9 Lecture 4 Lab 05"
author: 
  - "Team Member 1: NAME HERE"
  - "Team Member 2: NAME HERE"
  - "Team Member 3: NAME HERE"
date: today
date-format: "MMMM D[<sup style='font-size:65%;'>th</sup>], YYYY"
format: pdf
execute:
  echo: true
---


# What is One-Way ANOVA test?


Type your lecture notes here.


__When do we need to use this test, in general ?__

 
 Type your lecture notes here.

 
__What type of variables do we need to conduct this test?__


Type your lecture notes here.


# Case of this Lab

The Wolf River in Tennessee flows past an abandoned site once used by the pesticide industry for dumping wastes, including chlordane (pesticide), aldrin, and dieldrin (both insecticides). These highly toxic organic compounds can cause various cancers and birth defects. As these compounds are denser than water and their molecules tend to stick to particles of sediment, they are more likely to be found in higher concentrations near the bottom.

Now we are collecting a total of 30 random samples from this river to test if there is a difference between the mean aldrin concentrations among the three levels (surface, middepth, bottom)? (Set the alpha value as 0.05 for this study.)  

```{r}
# use my code available in slideshow. Please save both quarto document and csv file in your STAT 218 folder. Otherwise, the code will not work.
```


__Research Question of this study:__ Type your research question here. The information is available in your lecture notes.


## Steps for Conducting Hypothesis Testing for This Test

Run the Code Chunk below to load your data set as well as utilizing `library()` functions that you need.

```{r}
#| echo: true
#| output: false

library(tidyverse)
aldrin <- read_csv("aldrin.csv")

```


### Step 1. Formulate Hypotheses

__Write out the null & the alternative hypotheses within the context of this study:__

Type here.



### Step 2. Checking Conditions/Assumptions:

Type here.

```{r}
#| echo: true
#| output: true

# Type code here to check normality for each group in your categorical variable.

```

Interpret the assumptions overall here.

### Step 3.1 Conduct a One-Way ANOVA test and interpret the output



```{r}
#| echo: true
#| output: true
 
# Type your code here 

```


Type your interpretation here.


### Step 3.2 Conduct a Post Hoc analysis to determine which group(s) differ. 



```{r}
#| echo: true
#| output: true
 
# Type your code here 

```


Type your interpretation here.


### Step 4. Draw conclusion



__Conclusion Statement:__


Type your conclusions here.
