---
title: "STAT 218 Lab Assignment 2"
author: 
  - "Team Member 1: NAME HERE"
  - "Team Member 2: NAME HERE"
  - "Team Member 3: NAME HERE"
format: pdf
execute:
  echo: true
---


## Lab Assignment 2

In this assignment, we will work with the data available in the package of `palmerpenguins`. Please install and use that package if did not do it so far. 

And let's load our data into R by using data() function.Remember why we need to use library() function at the beginning of this document (I've added this for you, you're welcome!)

```{r}
library(tidyverse)
library(palmerpenguins)
data("penguins") 
```

__NOTE:__ Please ignore `penguins_raw` data for this class and USE `penguins` for this assignment.

__Question 1: Please use glimpse() function and write 2-3 sentences to explain what you see.__


```{r}

# Put your R Code Chunk here. 

```


Type your answer (2-3 sentences) here.


__Question 2: Choose a numeric variable from the dataset and create a histogram to visualize it. Provide an explanation of the observed distribution.__

```{r}

# Put your R Code Chunk here. 

```


Describe the patterns and insights you observe in the histogram.



__Question 3: Create a boxplot by using the variables species and bill_length_mm. Describe the graph using your own words.__


```{r}

# Put your R Code Chunk here. 

```

Describe the patterns and insights you observe in the boxplot.


__Question 4: Using the geom_point() function, plot a graph that shows the linear relationship between bill_length_mm and bill_depth_mm, coloring different species in that graph.__

```{r}

# Put your R Code Chunk here. 

```


Describe the patterns and insights you observe in the plot.

